RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data

### 2015-04-27 paper/paper7/paper7.tex
section 4

Bosch et al. identified 76 requirements to formulate RDF constraints (e.g. \emph{R-75, R-81: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each expressed by different constraint languages.
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.

We developed a system to classify RDF constraints and RDF constraint types.
Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
%\emph{data model specific constraint types} (e.g. \emph{data model consistency})

We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 213 constraints (classified as 53 distinct constraint types) to validate rectangular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}), and therefore apply the proposed classification system to several vocabularies to represent both data and metadata \cite{BoschZapilkoWackerowEckert2015}.
In this section, we describe constraints, which are important to ensure \emph{SBE} (meta)data quality, 
associate them with default severity levels, and assign them to $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraint types. 
\tb{Depending on individual use cases, validation environments should enable users to select which constraints to validate against.
For some use cases, validating $\mathcal{CT}_{B}$ constraints may be more important than validating $\mathcal{CT}_{S}$ or $\mathcal{CT}_{C}$ constraints.}

>>>>

Bosch et al. identified 76 requirements to formulate RDF constraints (e.g. \emph{R-75, R-81: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages.
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to \emph{DL} to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.

We developed a system to classify both RDF constraint types and RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary.
%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 213 constraints of 53 distinct constraint types 
to validate tabular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), and thesauri (\emph{SKOS}).
By applying the proposed classification system to several vocabularies to represent both metadata and data, we show its generality \cite{BoschZapilkoWackerowEckert2015}.

\tb{Depending on individual use cases, validation environments should enable users to select which constraints to validate against.
For some use cases, validating $\mathcal{CT}_{B}$ constraints may be more important than validating $\mathcal{CT}_{S}$ or $\mathcal{CT}_{C}$ constraints.}
